### 2018-08-29 sections/objects.tex
adding new textual changes

The event reconstruction is affected by multiple $pp$ collisions in a single bunch crossing and by collisions
in neighboring bunch crossings, referred to as ``pileup''. 
Interaction vertices from the $pp$ collisions are reconstructed from at least two tracks 
with transverse momentum ($\pt$) larger than $400~\mev$ that are consistent with originating from the 
beam collision region in the $x$--$y$ plane. If more than one primary vertex candidate is found, the
candidate whose associated tracks form the largest sum of squared $\pt$~\cite{ATL-PHYS-PUB-2015-026}
is selected as the hard-scatter primary vertex.

@@

Electron (muon) candidates are matched to the primary vertex by requiring that the significance of their transverse impact parameter, $d_0$, 
satisfies $|d_0/\sigma(d_0)|<5\,(3)$, where $\sigma(d_0)$ is the measured uncertainty in $d_0$,
and by requiring that their longitudinal impact parameter, $z_0$, satisfies $|z_0 \sin\theta|<0.5$~mm.
To further reduce the background from non-prompt leptons, photon conversions and hadrons, lepton candidates are also required to be isolated 
in the tracker and in the calorimeter.
A track-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$, where
the scalar sum includes all tracks (excluding the lepton candidate itself) within the cone defined by $\Delta R<R_{\textrm{cut}}$ about the %axis
direction of the lepton.  The value of $R_{\textrm{cut}}$ is the smaller of $r_{\textrm{min}}$ and $10~\gev/\pt^\ell$, where
$r_{\textrm{min}}$ is set to 0.2 (0.3) for electron (muon) candidates, and $\pt^\ell$ is the lepton $\pt$. 
The $\Hbb$ search requires lepton candidates to satisfy $I_R/\pt^\ell < 0.06$, while the $\Htautau$ search 
makes $\pt$-dependent requirements on $I_R/\pt^\ell$. Additionally, the $\Htautau$ search requires leptons to
satisfy a calorimeter-based isolation criterion: the sum of the transverse energy of
topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contributions
from pile-up and the energy deposit of the lepton itself, is required to be less than a $\pt$-dependent 
percentage of the lepton energy. 
%Additionally, the $\Htautau$ search requires leptons to
%satisfy a calorimeter-based isolation criterion; a requirement is made on the sum of the transverse energy of
%topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contribution
%from the energy deposit of the lepton itself and correcting for pile-up effects, to be less than a $\pt$-dependent 
%percentage of the lepton energy. 
%The combined efficiency of track-based and calorimeter-based isolation requirements made by the $\Htautau$ 
%search is 90\% (99\%) at $\pt=25\;(60)~\gev$.

>>>>

The event reconstruction is affected by multiple $pp$ collisions in a single bunch crossing and by collisions
in neighbouring bunch crossings, referred to as ``pile-up''. 
Interaction vertices from the $pp$ collisions are reconstructed from at least two tracks 
with transverse momentum ($\pt$) larger than $400~\mev$ that are consistent with originating from the 
beam collision region in the $x$--$y$ plane. If more than one primary vertex candidate is found, the
candidate whose associated tracks form the largest sum of squared $\pt$~\cite{ATL-PHYS-PUB-2015-026}
is selected as the hard-scatter primary vertex.

@@

Electron (muon) candidates are matched to the primary vertex by requiring that the significance of their transverse impact parameter, $d_0$, 
satisfies $|d_0/\sigma(d_0)|<5\,(3)$, where $\sigma(d_0)$ is the measured uncertainty in $d_0$,
and by requiring that their longitudinal impact parameter, $z_0$, satisfies $|z_0 \sin\theta|<0.5$~mm.
To further reduce the background from non-prompt leptons, photon conversions and hadrons, lepton candidates are also required to be isolated 
in the tracker and in the calorimeter.
A track-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$, where
the scalar sum includes all tracks (excluding the lepton candidate itself) within the cone defined by $\Delta R<R_{\textrm{cut}}$ about the %axis
direction of the lepton.  The value of $R_{\textrm{cut}}$ is the smaller of $r_{\textrm{min}}$ and $10~\gev/\pt^\ell$, where
$r_{\textrm{min}}$ is set to 0.2 (0.3) for electron (muon) candidates, and $\pt^\ell$ is the lepton $\pt$. 
The $\Hbb$ search requires lepton candidates to satisfy $I_R/\pt^\ell < 0.06$, while the $\Htautau$ search 
makes $\pt$-dependent requirements on $I_R/\pt^\ell$. Additionally, the $\Htautau$ search requires leptons to
satisfy a calorimeter-based isolation criterion: the sum of the transverse energy within a cone of
$\Delta R<0.2$ around the lepton, after subtracting the contributions
from pile-up and the energy deposit of the lepton itself, is required to be less than a $\pt$-dependent 
percentage of the lepton energy. 
%Additionally, the $\Htautau$ search requires leptons to
%satisfy a calorimeter-based isolation criterion; a requirement is made on the sum of the transverse energy of
%topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contribution
%from the energy deposit of the lepton itself and correcting for pile-up effects, to be less than a $\pt$-dependent 
%percentage of the lepton energy. 
%The combined efficiency of track-based and calorimeter-based isolation requirements made by the $\Htautau$ 
%search is 90\% (99\%) at $\pt=25\;(60)~\gev$.

### 2018-08-29 sections/signal_background_modeling.tex
adding new textual changes

All simulated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
To model the effects of pileup, events from minimum-bias interactions are generated using the {\pythia}~8.186~\cite{Sjostrand:2007gs} 
event generator and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
The generated events are processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
using \textsc{Geant4}~\cite{Agostinelli:2002hh}. A faster simulation, where the full \textsc{Geant4} simulation of
the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
is adopted for some of the samples used to estimate systematic uncertainties.
Simulated events are processed through the same reconstruction software as the data, and corrections are applied so that the object identification 
efficiencies, energy scales and energy resolutions match those determined from data control samples.

@@

This background is estimated directly from data by defining control regions (CR) enriched in fake $\tauhad$ candidates via loosened $\tauhad$ requirements. These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}. The CR selection requirements are analogous to those used to define the different SRs, except that the leading (trailing) $\tauhad$ candidate 
in the $\lephad$ ($\hadhad$) channel is required to be of loose-not-medium quality, and the requirement on its charge is dropped.

>>>>

All simulated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
To model the effects of pile-up, events from minimum-bias interactions are generated using the {\pythia}~8.186~\cite{Sjostrand:2007gs} 
event generator and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
The generated events are processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
using \textsc{Geant4}~\cite{Agostinelli:2002hh}. A faster simulation, where the full \textsc{Geant4} simulation of
the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
is adopted for some of the samples used to estimate systematic uncertainties.
Simulated events are processed through the same reconstruction software as the data, and corrections are applied so that the object identification 
efficiencies, energy scales and energy resolutions match those determined from data control samples.

@@

This background is estimated directly from data by defining control regions (CR) enriched in fake $\tauhad$ candidates via loosened $\tauhad$ requirements. These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}. The CR selection requirements are analogous to those used to define the different SRs, except that the leading (trailing) $\tauhad$ candidate 
in the $\lephad$ ($\hadhad$) channel is required to be of loose-not-medium quality, and the requirement on its charge is removed.

### 2018-08-29 sections/statistical_analysis.tex
adding new textual changes

For each search, the final discriminant distributions across all analysis regions considered are jointly analysed to test for the 
presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a multiplicative factor to the yield for $\Hq$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$,
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties in the signal and background expectations. 
Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are implemented in the likelihood function as Gaussian or log-normal constraints, with the exception of a few parameters 
that control the normalisation of the some of the background components (e.g. the \ttbin\ background in the case of the $\Hbb$ search), which 
are treated as free parameters in the fit.

>>>>

For each search, the final discriminant distributions across all analysis regions considered are jointly analysed to test for the 
presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a multiplicative factor to the yield for $\Hq$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$,
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties in the signal and background expectations. 
Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are implemented in the likelihood function as Gaussian or log-normal constraints, with the exception of a few parameters 
that control the normalisation of some background components (e.g. the \ttbin\ background in the case of the $\Hbb$ search), which 
are treated as free parameters in the fit.

### 2018-08-29 sections/strategy_Hbb.tex
adding new textual changes

The overall rate and composition of the $\ttbar$+jets background strongly depends on the jet and $b$-tag 
multiplicities, as illustrated in Figure~\ref{fig:Hbb_Summary}.
Regions with exactly two $b$-tagged jets are dominated by $\ttbar$+light jets, while regions with 
at least four $b$-tagged jets are dominated by \ttbin. Intermediate compositions are found in regions with exactly three 
$b$-tagged jets.  Most of the $\ttbar$+light-jets background in the these regions has a charm jet from the hadronic $W$ boson 
decay  being $b$-tagged, in addition to the two $b$-jets from the top quark decays.

>>>>

The overall rate and composition of the $\ttbar$+jets background strongly depends on the jet and $b$-tag 
multiplicities, as illustrated in Figure~\ref{fig:Hbb_Summary}.
Regions with exactly two $b$-tagged jets are dominated by $\ttbar$+light jets, while regions with 
at least four $b$-tagged jets are dominated by \ttbin. Intermediate compositions are found in regions with exactly three 
$b$-tagged jets.  Most of the $\ttbar$+light-jets background in these regions has a charm jet from the hadronic $W$ boson 
decay  being $b$-tagged, in addition to the two $b$-jets from the top quark decays.

### 2018-08-29 sections/systematic_uncertainties.tex
adding new textual changes

The uncertainty in the integrated luminosity is 2.1\%, affecting the overall normalisation of
all processes estimated from the simulation. It is derived, following a methodology similar to that detailed in Ref.~\cite{Aaboud:2016hhf}, 
from a preliminary calibration of the luminosity scale using $x$--$y$ beam-separation scans performed in August 2015 and May 2016.

@@

Uncertainties associated with jets arise from the jet energy scale
and resolution, and the efficiency to pass the JVT requirements. 
The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pileup treatment, 
is split into 21 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}.

@@

Uncertainties on the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah},
as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}
(it is assumed that two jets come from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the selected jet multiplicity,  
i.e. 34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively.
Recent comparisons between data and {\sherpa}~2.1.1 for $WZ(\to \ell\nu\ell\ell) + \geq$4 jets show
agreement within the experimental uncertainty of approximately 40\%~\cite{Aaboud:2016yus}, which further justifies the above uncertainty.

>>>>

The uncertainty in the integrated luminosity is 2.1\%, affecting the overall normalisation of
all processes estimated from the simulation. It is derived, following a methodology similar to that detailed in Ref.~\cite{Aaboud:2016hhf}, 
from a calibration of the luminosity scale using $x$--$y$ beam-separation scans performed in August 2015 and May 2016.

@@

Uncertainties associated with jets arise from the jet energy scale
and resolution, and the efficiency to pass the JVT requirements. 
The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pile-up treatment, 
is split into 21 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}.

@@

Uncertainties on the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah},
as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}
(it is assumed that two jets originate from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the selected jet multiplicity,  
i.e. 34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively.
Recent comparisons between data and {\sherpa}~2.1.1 for $WZ(\to \ell\nu\ell\ell) + \geq$4 jets show
agreement within the experimental uncertainty of approximately 40\%~\cite{Aaboud:2016yus}, which further justifies the above uncertainty.
